% Copyright (C) 2021 Biren Patel
% Resume

%------------------------------------------------------------------------------%
% preamble
%------------------------------------------------------------------------------%

\documentclass [
        11pt
] {article}

\usepackage [
        utf8
] {inputenc}

%------------------------------------------------------------------------------%
% paper geometry
%------------------------------------------------------------------------------%

\usepackage [
        a4paper,
        noheadfoot = true,
        left = 0.5in,
        right = 0.5in,
        top = 0.5in,
        bottom = 0.5in,
] {geometry}

%------------------------------------------------------------------------------%
% style tools
%------------------------------------------------------------------------------%

\usepackage {multicol}

\usepackage [
        dvipsnames
] {xcolor}

\definecolor{green}{RGB}{35,113,114} %forest green with a subtle note of pine

\pagenumbering{gobble} %turn off page num at footer

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

%------------------------------------------------------------------------------%
% introduction
%------------------------------------------------------------------------------%

\begin{document}

\begin{multicols}{2}

\noindent {\huge BIREN PATEL}\\
\noindent \textcolor{green}{LOCATION $ \boldsymbol{\cdot} $ CITIZENSHIP}\\
	\noindent \textcolor{green}{PHONE_NUMBER}\\

\columnbreak

\hspace*{\fill} \noindent \textcolor{green}{biren.dilip.patel@gmail.com}\\
\hspace*{\fill} \noindent \textcolor{green}{github.com/birendpatel}\\
\hspace*{\fill} \noindent \textcolor{green}{linkedin.com/in/birendilippatel}

\end{multicols}

%-----------------------------------------------------------------------------%
% summary 
%------------------------------------------------------------------------------%

\noindent\textcolor{green}{SUMMARY \rule{16.35cm}{1pt}}

\vspace*{10pt}

\noindent I am a software developer with 5 years of experience in data science, 
data engineering, and databases. My recent professional work focused on data
warehousing and machine learning in Python and SQL.

\vspace*{10pt}


%------------------------------------------------------------------------------%
% skills
%------------------------------------------------------------------------------%

\noindent\textcolor{green}{SKILLS \rule{17cm}{1pt}}

\begin{multicols}{4}

\centering{\noindent \textbf {Programming}}\\
\centering{\noindent Python}\\
\centering{\noindent Go}\\
\centering{\noindent C}\\

\columnbreak

\centering{\noindent \textbf {Business Intelligence}}\\
\centering{\noindent Power BI}\\
\centering{\noindent Tableau}\\
\centering{\noindent SQL }\\

\columnbreak

\centering{\noindent \textbf {Databases}}\\
\centering{\noindent SQL Server}\\
\centering{\noindent Oracle}\\
\centering{\noindent SQLite}\\

\columnbreak

\centering{\noindent \textbf {Mathematics}}\\
\centering{\noindent Probability Theory}\\
\centering{\noindent Linear Algebra}\\
\centering{\noindent Statistics}

\end{multicols}

%------------------------------------------------------------------------------%
% experience
%------------------------------------------------------------------------------%

\noindent\textcolor{green}{EXPERIENCE \rule{15.8cm}{1pt}}

\vspace*{10pt}

\noindent \textbf {Database Analyst,} The University of Texas at Austin
\hspace*{\fill} \textbf{Dec 2018 - May 2021}

\begin{itemize}[itemsep=1pt,topsep=1pt]
\renewcommand{\labelitemi}{\scriptsize$\blacksquare$}

\item Created a 94$\%$-accurate natural language processing system which used a PyTorch
neural network to analyse unstructured text, classify potential donors, and
feed results to a Tableau dashboard.

\item Developed scoring models and recommendation systems in Scikit-Learn with
logistic regression, decision trees, and k-means clustering. 

\item Designed star and snowflake database schemas and ERD diagrams for a new Azure data
warehouse to help support downstream analytics and machine learning.

\item Implemented a data warehouse in Oracle to replace a legacy SAS data
pipeline and adhered to good software engineering practices such as Git version control,
unit testing, and CI/CD.

\item Eliminated manual workflows in the data analytics team by developing Python modules 
for database driver abstraction, SQL static analysis, and automated hyperparameter tuning.

\end{itemize}

\vspace*{5pt}




\noindent \textbf{SQL Developer,} Bluebonnet Trails Community Services
\hspace*{\fill} \textbf{Mar 2016 - Jul 2017}

\begin{itemize}[itemsep=1pt,topsep=1pt]
\renewcommand{\labelitemi}{\scriptsize$\blacksquare$}

\item Introduced Power BI into the reporting infrastructure and built an ETL
pipeline in SQL Server to funnel data into curated Power BI dashboards for 
the board of directors.

\item Wrote 80+ stored procedures, views, SSRS reports, and ad-hoc
MS SQL queries for 8 departments.

\end{itemize}

\vspace*{5pt}








\noindent \textbf{Research Assistant,} The University of Texas at Austin
\hspace*{\fill} \textbf{Jan 2015 - May 2015}

\begin{itemize}[itemsep=1pt,topsep=1pt]
\renewcommand{\labelitemi}{\scriptsize$\blacksquare$}

\item Assisted graduate biomechanics research by calibrating Vicom motion 
capture systems, validating real-time data, and performing surface EMG tests.

\end{itemize}

\vspace*{10pt}

%-----------------------------------------------------------------------------%
% projects 
%------------------------------------------------------------------------------%

\noindent\textcolor{green}{PROJECTS \rule{16.3cm}{1pt}}

\vspace*{10pt}

\noindent \textbf {Lemon,} \href{https://github.com/birendpatel/lemon}{github.com/birendpatel/lemon}
\hspace*{\fill} \textbf{Aug 2021 - Jan 2022}

\begin{itemize}[noitemsep,topsep=0pt]
\renewcommand{\labelitemi}{\scriptsize$\blacksquare$}

\item Built a programming language in C with features such as an optimizing
compiler, garbage collection, static typing, and object orientation.

\vspace*{5pt}

\item Developed utilities in C and Python to support error logging, JSON serialization,
automatic dependency management, metaprogramming, and integration tests.

\end{itemize}

\vspace*{10pt}

%------------------------------------------------------------------------------%
% education
%------------------------------------------------------------------------------%

\noindent\textcolor{green}{EDUCATION \rule{16cm}{1pt}}

\vspace*{10pt}

\noindent \textbf {MSc Data Science,} City University of London
\hspace*{\fill} \textbf{Sep 2017 - Nov 2018}

\begin{itemize}[noitemsep,topsep=0pt]
\renewcommand{\labelitemi}{\scriptsize$\blacksquare$}
\item Thesis: Wrote mathematical proofs and developed Monte Carlo simulations
in NumPy and SciPy to analyze the statistical behavior of genetic algorithms.
Awarded with distinction.
\end{itemize}

\noindent \textbf {BSc Kinesiology,} The University of Texas at Austin
\hspace*{\fill} \textbf{Aug 2011 - Dec 2015}

\end{document}
